---
title: "dolrother"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dolrother}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Other Datasets

For official documentation go to: https://developer.dol.gov/others/

### Agency

```{r, error=TRUE}
library(dolr)

dolsetkey("3e28950b-f0f0-4ba1-b7ec-e4ce5c112779")

head(dol_oth(dataset = 10, sheet = 1))

```

### Research And Evaluation Inventory

```{r, error=TRUE}

head(dol_oth(dataset = 5, sheet = 1))

```

### Geography 

```{r, error=TRUE}

head(dol_oth(dataset = 6, sheet = 1))

```

## Datasets and Sheets

**'dataset'**:
   1) Sweat & Toil 
      **'sheet'**:
        1) SweatToilAllRegions
        2) SweatToilAllCountries
        3) SweatToilAllTerritories
        4) SweatToilAllAdvancementLevels
        5) SweatToilAllAssessments
        6) SweatToilAllSectors
        7) SweatToilAllGoods
        8) SweatToilAllCountryGoods
        9) SweatToilAllStatistics
        10) SweatToilAllConventions
        11) SweatToilAllSuggestedActions
        12) SweatToilAllLegalStandards
        13) SweatToilAllEnforcements
        14) SweatToilMechanisms
   2) VETS4212
      **'sheet'**:
        1) V4212DataDotGov
   3) VETS100 
      **'sheet'**:
        1) V100DataDotGov
        2) V100ADataDotGov
   4) API Metrics (per key) 
      **'sheet'**:
        1) NumberOfRequestsPerKeys
        2) NumberOfRequestsPerDayByKeys
        3) NumberOfRequestsPerMonthByKeys
        4) NumberOfRequestsPerYearByKeys
        5) NumberOfRequestsPerYearByWeeks
        6) TopDatasetsPerKeys
        7) TopDatasetsPerYearPerKeys
        8) TopDatasetsPerMonthPerKeys
        9) TopDatasetsPerWeekPerKeys
        10) TopDatasetsPerDayPerKeys
        11) TopDataTablesPerKeys
        12) TopDataTablesPerKeyDays
        13) TopDataTablesPerKeyMonths
        14) TopDataTablesPerKeyWeeks
        15) TopDataTablesPerKeyYears
   5) Research And Evaluation Inventory 
      **'sheet'**:
        1) researchEvaluationInventory
   6) Geography 
      **'sheet'**:
        1) City
        2) CongressDistrict
        3) County
        4) State
   7) Form 
      **'sheet'**:
        1) Agencies
        2) AgencyForms
   8) Frequently Asked Questions (FAQ)
      **'sheet'**:
        1) Topics
        2) SubTopics
        3) TopicQuestions
   9) API Metadata 
      **'sheet'**:
        1) APIMetadatas
   10) Agency
      **'sheet'**:
        1) Agencies
