---
title: "dolrwagehour"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dolrwagehour}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Wage and Hour Division

For official documentation go to: https://developer.dol.gov/wage-and-hour-division/

### WHD Compliance V1

```{r, error=TRUE}
library(dolr)

dolsetkey("3e28950b-f0f0-4ba1-b7ec-e4ce5c112779")

dol_whd(dataset = 3, sheet = 4)

```

### Farm Labor Contractor and Farm Labor Contractor Employee

```{r, error=TRUE}

dol_whd(dataset = 2, sheet = 1)

```

## Datasets and Sheets

**'dataset'**:
   1) Farm Labor Contractor and Farm Labor Contractor Employee
      **'sheet'**:
        1) Farm Labor Contractors
        2) Farm Labor Contractor Employees
   2) Farm Labor Contractor and Farm Labor Contractor Employee 
      **'sheet'**:
        1) PublicationsView
        2) DocumentsView
   3) WHD Compliance V1
      **'sheet'**:
        1) full
        2) foodservice
        3) hospitality
        4) retail
