---
title: "Expanding Growth Opportunities and Learnings"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dolrgrowthlearning}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Examples

The code chunks below shows how to query the Expanding Growth Opportunities and Learnings datasets available. 
For official documentation go to: https://developer.dol.gov/expanding-growth/

### OUI Initial Claims
```{r, error=TRUE, warning=FALSE}
library(dolr)
library(stringr)
library(knitr)

# Set the key
dolsetkey("3e28950b-f0f0-4ba1-b7ec-e4ce5c112779")

# The second dataset corresponds to 'OUI Initial Claims'
# The sheets shown are 1) unemploymentInsuranceInitialClaims
kable(head(str_trunc(dol_gol(dataset = 2, sheet = 1), 10, ellipsis = "..."))[1:4])

# To get the output in R, just use:
# x <- dol_gol(dataset = 2, sheet = 1)
```

### IPIA
```{r, error=TRUE, warning=FALSE}

# The third dataset corresponds to 'IPIA'
# The sheets shown are 1) causeByState ...
kable(head(str_trunc(dol_gol(dataset = 3, sheet = 1), 10, ellipsis = "..."))[1:7])

# ... 3) rate
kable(head(str_trunc(dol_gol(dataset = 3, sheet = 3), 10, ellipsis = "..."))[1:7])

# To get the output in R, just use:
# x <- dol_gol(dataset = 3, sheet = 3)
```

### Consumer Price Indexes (CPI)
```{r, error=TRUE, warning=FALSE}

# The third dataset corresponds to 'Consumer Price Indexes'
# The sheets shown are 1) CU_AREA 
kable(head(str_trunc(dol_gol(dataset = 8, sheet = 1), 10, ellipsis = "..."))[1:7])

# To get the output in R, just use:
# x <- dol_gol(dataset = 8, sheet = 1)
```

## Datasets and Sheets

```{r, error=TRUE, echo=FALSE}


```


**'dataset'**:
   1) Public Workforce System
      **'sheet'**:
        1) esFinal
        2) model
        3) recessionPeriods
   2) OUI Initial Claims
      **'sheet'**:
        1) unemploymentInsuranceInitialClaims
   3) IPIA
      **'sheet'**:
        1) causeByState
        2) causeByStateSummary
        3) rate
        4) rateSummary
   4) Quarterly Census Employment and Wage (CEW)
      **'sheet'**:
        1) EN_AREA
        2) EN_FOOTNOTE
        3) EN_INDUSTRY
        4) EN_LQAREA
        5) EN_OWNER
        6) EN_STATE
        7) EN_TYPE
   5) Occupational Employment Statistics Survey (OES)
      **'sheet'**:
        1) OE_AREA
        2) OE_AREATYPE
        3) OE_DATA_PUB
        4) OE_DATATYPE
        5) OE_FOOTNOTE
        6) OE_INDUSTRY
        7) OE_OCCUPATION
        8) OE_RELEASE
        9) OE_SEASONAL
        10) OE_SECTOR
        11) OE_SERIES
   6) Current Population Survey (CPS) 
      **'sheet'**:
        1) LE_AGES
        2) LE_BORN
        3) LE_CLASS
        4) LE_DATA_PUB
        5) LE_EARN
        6) LE_EDUCATION
        7) LE_FIPS
        8) LE_FOOTNOTE
        9) LE_INDY
        10) LE_LFST
        11) LE_OCCUPATION
        12) LE_ORIG
        13) LE_PCTS
        14) LE_RACE
        15) LE_SEASONAL
        16) LE_SERIES
        17) LE_SEXS
        18) LE_TDATA
        19) LE_UNIN
   7) Current Employment Statistics (CES)
      **'sheet'**:
        1) CE_DATA_PUB
        2) CE_DATATYPE
        3) CE_FOOTNOTE
        4) CE_INDUSTRY
        5) CE_SEASONAL
        6) CE_SERIES
        7) CE_SUPERSECTOR
   8) Consumer Price Indexes (CPI)
      **'sheet'**:
        1) CU_AREA
        2) CU_BASE
        3) CU_DATA_PUB
        4) CU_FOOTNOTE
        5) CU_ITEM
        6) CU_PERIODICITY
        7) CU_SEASONAL
        8) CU_SERIES
   9) 2010 Workforce Investment Act 
      **'sheet'**:
        1) workforceInvestmentAct
        2) workforceInvestmentActUi
        3) workforceInvestmentActWages
        4) lookup codes
   10) 2010 Occupational Employment Statistics
      **'sheet'**:
        1) area
        2) area_definitions
        3) areatype
        4) data
        5) datatype
        6) footnote
        7) industry
        8) industry_titles
        9) occugroup
        10) occupation
        11) occupation_definitions
        12) release
        13) seasonal
        14) sector
        15) series
        16) statemsa
   11) BLS Numbers 
      **'sheet'**:
        1) averageHourlyEarnings
        2) consumerPriceIndex
        3) employmentCostIndex
        4) exportPriceIndex
        5) importPriceIndex
        6) payrollEmployment
        7) producerPriceIndex
        8) productivity
        9) unemploymentRate
        10) averageHourlyEarnings12MonthChange
        11) averageHourlyEarnings1MonthChange
        12) averageHourlyEarnings1MonthNetChange
        13) consumerPriceIndex12MonthChange
        14) consumerPriceIndex1MonthChange
        15) exportPriceIndex12MonthChange
        16) exportPriceIndex1MonthChange
        17) importPriceIndex12MonthChange
        18) importPriceIndex1MonthChange
        19) payrollEmployment12MonthChange
        20) payrollEmployment12MonthNetChange
        21) payrollEmployment1MonthChange
        22) payrollEmployment1MonthNetChange
        23) producerPriceIndex12MonthChange
        24) producerPriceIndex1MonthChange
        25) unemploymentRate12MonthChange
        26) unemploymentRate1MonthChange
