---
title: "Onmi Query"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{omni}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Details

Although this library contain specific functions for querying each individual
grouping of datasets defined by the DOL, here shows an example of an omni 
function that will detect the dataset and sheet you want. This takes two string inputs,
the name of the dataset and sheet. This can detect abbreviations for some datasheets,
but should be exactly the same as provide on https://developer.dol.gov/. There is a 
mechanism in place to help correct errors in input.
I recommend using this as a quick and easy method of gaining access to data.
However, there is an additional overhead cost so this will be slower.

Currently a few of the APIs provided by the DOL are up to date or are possibly
broken. I recommend going https://devtools.dol.gov/APISampler/Home/Index and
seeing if you can query the data here. If not, then it likely broken here too.

### Querying the Gulf Oil Spill Dataset and OSHA_Direct_Read_Sampling sheet.

```{r, eval=FALSE}
library(dolr)
dol("Gulf Oil Spill", "OSHA_Direct_Read_Sampling")
```

### Querying the OUI Initial Claims Dataset and unemploymentInsuranceInitialClaims sheet.

```{r, eval=FALSE}
library(dolr)
dol("OUI Initial Claims", "unemploymentInsuranceInitialClaims")
```
