---
title: "setup"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{setup}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Setup

You can install the development version from GitHub with:

```{r, warning=FALSE, results='hide',message=FALSE}
# install.packages("devtools")
library(devtools)
devtools::install_github("etam4260/dolr")
```

The US Department of Labor requires users to gain an 
access key before querying their systems. You must go to 
https://devtools.dol.gov/developer and make an account.

From there you need to make a new token. Make sure to save the token somewhere as
you will only be able to view it once. However, you can use it as many times as you want.
You can now supply the 'key' argument.

To reduce the need to supply the key in every function call, you can use the 
dolsetkey(key) function to save the key to the package environment.

```{r}
library(dolr)

# The function will not output anything. 
dolsetkey("3e28950b-f0f0-4ba1-b7ec-e4ce5c112779")

# To check the current key.
# print(dolgetkey())
```

You can now access the API from the DOL. I recommend taking a look at the other
articles to get a better sense of how to access specific datasets. For more 
details on what datasets are available and their official documentation, go to https://developer.dol.gov/beginner/

