---
title: "Wage and Hour Division"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dolrwagehour}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Examples

The code chunks below shows how to query the Wage and Hour Division datasets available. 
For official documentation go to: https://developer.dol.gov/wage-and-hour-division/

### WHD Compliance 

```{r, error=TRUE, warning=FALSE}
library(dolr)
library(stringr)
library(knitr)

# Set the key
dolsetkey("3e28950b-f0f0-4ba1-b7ec-e4ce5c112779")

# This queries WHD Compliance datasets. 
# This gets the sheet associated with retail.
kable(head(str_trunc(dol_whd(dataset = 3, sheet = 4), 10, ellipsis = "..."))[1:7])

# To get the output in R, just use:
# x <- dol_whd(dataset = 3, sheet = 4)
```

### Wage and Hour Publications System 

```{r, error=TRUE, warning=FALSE}

# This queries the Wage and Hour Publications System 
# This get the sheet associated with: PublicationsView
kable(head(str_trunc(dol_whd(dataset = 2, sheet = 1), 10, ellipsis = "..."))[1:7])

# To get the output in R, just use:
# x <- dol_whd(dataset = 2, sheet = 1)
```

## Datasets and Sheets


```{r, error=TRUE, echo=FALSE}


```


**'dataset'**:
   1) Farm Labor Contractor and Farm Labor Contractor Employee
      **'sheet'**:
        1) Farm Labor Contractors
        2) Farm Labor Contractor Employees
   2) Wage and Hour Publications System 
      **'sheet'**:
        1) PublicationsView
        2) DocumentsView
   3) WHD Compliance V1
      **'sheet'**:
        1) full
        2) foodservice
        3) hospitality
        4) retail
